Figures

### 2019-04-09 code/figures.rmd
Dropped z-transformation of biserial correlation. Now r only effect size
Z-transformation not recommended by Jacobs and Viechtbauer (2017) for biserial correlations, p. 176

```{r MA_df}
summarizer <- function(x){
  fit <- rma(measure = "ZCOR", ri = x$r, ni = x$n, data = x) #takes raw correlation as input
  fitr <- rma(yi = x$r, vi = x$vi, data = x)
  data.frame(z = fit$b[[1]], I2 = fit$I2, H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1),
             r = fitr$b[[1]], tau2r = fitr$I2) #estimates out
}
#Default method of metafor for calculating H2 is truncated at one. Alternative method for calculating H2 provides information also on excessive homogeneity, i.e, less variability than expected by chance (that is, does not have a lower limit of 1). This method approximates H2 as if we were using the Dersimonian and Laird estimate of tau2, although we use REML. See Higgins & Thompson, 2002 and ?print.rma.uni.

@@

res2 <- res %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(summarizer, .id = "effect") %>% 
  mutate(z = abs(z), r = abs(r)) #Absolute values since we are interested in effect size rather than direction
```

```{r cor_het_effect_size, results = "hide", cache=TRUE}
#Basic correlations
cor.test(res2$I2, res2$z) #pearson I2

I2_fit <- summary(lm(I2 ~ z, data = res2)) #for annotating figures

@@

cor.test(res2$H2, res2$z) #pearson H2

H2_fit <- summary(lm(H2 ~ z, data = res2))

cor.test(res2$I2, res2$z, method = "spearman") #spearman

@@

cor.test(dropped_anchoring$I2, dropped_anchoring$z) #pearson

@@

#I2
pear <- function(formula, data, indices){ #pearson
     d <- data[indices,]
     fit <- cor.test(formula = ~ I2 + z, data=d)
     return(fit$estimate)
}

bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ z + I2)

@@

spear <- function(formula, data, indices){ #spearman
     d <- data[indices,]
     fit <- cor.test(formula = ~ I2 + z, data=d, method = "spearman")
     return(fit$estimate)
}

options(warn=-1)
bootfit <- boot(data=res2, statistic=spear, R=1000, formula= ~ z + I2)
options(warn=0)

@@

#Excluding anchoring effects
bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ z + I2)

@@

#H2
pear <- function(formula, data, indices){
     d <- data[indices,]
     fit <- cor.test(formula = ~ H2 + z, data=d)
     return(fit$estimate)
}

bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ z + H2)

@@

#Plots of H2 and I2 vs. fisher's z for all effects together

I2 <- ggplot(res2, aes(x = z, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  coord_cartesian(ylim = c(0, 100)) +
  geom_text(x = 0.15, y = 80, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
  scale_x_continuous(name = expression(paste("Effect size (Fisher's ", italic(z), ")")))

H2 <- ggplot(res2, aes(x = z, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  geom_text(x = 0.14, y = 5.9, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
  scale_x_continuous(name = expression(paste("Effect size (Fisher's ", italic(z),")")))

@@

```{r r_vs_tau2, fig.asp = 0.618, cache = TRUE}
r_tau2 <- ggplot(res2, aes(x = r, y = tau2r)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  geom_text(x = 0.14, y = 75, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = expression(paste("Point-biserial correlation ", italic(r))))

>>>>

```{r MA_df}
summarizer <- function(x){#Z-transformation not recommended by Jacobs and Viechtbauer (2017) for biserial correlations, p. 176
  fitr <- rma(yi = x$r, vi = x$vi, data = x) #rma for biserial and pearson correlations (distinct per effect!)
  data.frame(r = fitr$b[[1]], tau2r = fitr$tau2, I2 = fitr$I2, H2trunc = fitr$H2, H2 = fitr$QE / (fitr$k - 1)) 
}
#Default method of metafor for calculating H2 is truncated at one. Alternative method for calculating H2 provides information also on excessive homogeneity, i.e, less variability than expected by chance (that is, does not have a lower limit of 1). This method approximates H2 as if we were using the Dersimonian and Laird estimate of tau2, although we use REML. See Higgins & Thompson, 2002 and ?print.rma.uni.

@@

res2 <- res %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(summarizer, .id = "effect") %>% 
  mutate(r = abs(r)) #Absolute values since we are interested in effect size rather than direction
```

```{r cor_het_effect_size, results = "hide", cache=TRUE}
#Basic correlations
cor.test(res2$I2, res2$r) #pearson I2

I2_fit <- summary(lm(I2 ~ r, data = res2)) #for annotating figures

@@

cor.test(res2$H2, res2$r) #pearson H2

H2_fit <- summary(lm(H2 ~ r, data = res2))

cor.test(res2$I2, res2$r, method = "spearman") #spearman

@@

cor.test(dropped_anchoring$I2, dropped_anchoring$r) #pearson

@@

#I2
pear <- function(formula, data, indices){ #pearson
     d <- data[indices,]
     fit <- cor.test(formula = ~ I2 + r, data=d)
     return(fit$estimate)
}

bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ r + I2)

@@

spear <- function(formula, data, indices){ #spearman
     d <- data[indices,]
     fit <- cor.test(formula = ~ I2 + r, data=d, method = "spearman")
     return(fit$estimate)
}

options(warn=-1)
bootfit <- boot(data=res2, statistic=spear, R=1000, formula= ~ r + I2)
options(warn=0)

@@

#Excluding anchoring effects
bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ r + I2)

@@

#H2
pear <- function(formula, data, indices){
     d <- data[indices,]
     fit <- cor.test(formula = ~ H2 + r, data=d)
     return(fit$estimate)
}

bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ r + H2)

@@

#Plots of H2 and I2 vs. biserial correlation r for all effects together

I2 <- ggplot(res2, aes(x = r, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  coord_cartesian(ylim = c(0, 100)) +
  geom_text(x = 0.14, y = Inf, vjust = 7, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
  scale_x_continuous(name = expression(paste("Biserial correlation ", italic(r))))

H2 <- ggplot(res2, aes(x = r, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
  scale_x_continuous(name = expression(paste("Biserial correlation ", italic(r))))

@@

```{r r_vs_tau2, fig.asp = 0.618, cache = TRUE}
r_tau2 <- ggplot(res2, aes(x = r, y = tau2r)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = expression(paste("Biserial correlation ", italic(r))))
